An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-06 ex3/paper/paper.tex
Modified pdp/adv plots

\subsection{Evaluation}
\begin{figure*}
\includegraphics[width=0.45\textwidth]{adv_plots/cwl1.pdf}
\includegraphics[width=0.45\textwidth]{adv_plots/cwl2.pdf}
\caption{Performance of the \gls{cw} with different $\epsilon$ values for $\ell_1$ and $\ell_2$ distances.}
\label{fig:adv_cw}
\end{figure*}
\autoref{fig:adv_cw} depicts the ratio of attack flows which were successfully misclassified as benign with respect to the final packet along with the resulting distance from the original sample. Evidently, the larger the $\epsilon$ parameter, the better the attack works, but also the distances become larger.

@@

\begin{figure*}
\includegraphics[width=0.45\textwidth]{adv_plots/fgsm.pdf}
\includegraphics[width=0.45\textwidth]{adv_plots/l_inf_pgd.pdf}
\caption{Performance of FSGM and $\ell_\infty$-bounded \gls{pgd} for different bounds.}
\label{fig:fgsm}
\end{figure*}

@@

\subsubsection{Results}
Table~\ref{fig:featRandom} shows our results. The results match to a large extent with the expectations one has when classifying network flows. In particular, the most important features turn out to be the used protocol, packet length and the SYN TCP flag. While the first two features are essential for characterizing flows, a high number of packets with set SYN flag is an important characteristic for port scanning or certain DoS attacks. Also the fact that most of TCP flags do not play an important role in our dataset was expected. It is interesting to note, however, that the interarrival time of packets does not play a crucial role for the detection of attacks.

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{{"../plots/plot2/flows_full_no_ttl_pred_plots2_outcomes_0_3.pickle_0_Botnet-ARES"}.pdf}
\includegraphics[width=0.48\textwidth]{{"../plots/plot2/flows_full_no_ttl_pred_plots2_outcomes_0_3.pickle_7_DoS - DDoS-DoS slowloris"}.pdf}
\includegraphics[width=0.48\textwidth]{{"../plots/plot2/flows_full_no_ttl_pred_plots2_outcomes_0_3.pickle_11_PortScan-PortScan - Firewall off"}.pdf}
\includegraphics[width=0.48\textwidth]{{"../plots/plot2/flows_full_no_ttl_pred_plots2_outcomes_0_3.pickle_1_Brute Force-FTP-Patator"}.pdf}

>>>>

\subsection{Evaluation}
% \begin{figure*}
% \includegraphics[width=0.45\textwidth]{adv_plots/cwl1.pdf}
% \includegraphics[width=0.45\textwidth]{adv_plots/cwl2.pdf}
% \caption{Performance of the \gls{cw} with different $\epsilon$ values for $\ell_1$ and $\ell_2$ distances.}
% \label{fig:adv_cw}
% \end{figure*}
\autoref{fig:adv_cw} depicts the ratio of attack flows which were successfully misclassified as benign with respect to the final packet along with the resulting distance from the original sample. Evidently, the larger the $\epsilon$ parameter, the better the attack works, but also the distances become larger.

@@

% \begin{figure*}
% \includegraphics[width=0.45\textwidth]{adv_plots/fgsm.pdf}
% \includegraphics[width=0.45\textwidth]{adv_plots/l_inf_pgd.pdf}
% \caption{Performance of FSGM and $\ell_\infty$-bounded \gls{pgd} for different bounds.}
% \label{fig:fgsm}
% \end{figure*}

@@

\subsubsection{Results}
\begin{figure*}
\includegraphics[width=.49\textwidth]{figures/feat_imp_flow_2017.pdf}\hspace{.02\textwidth}
\includegraphics[width=.49\textwidth]{figures/feat_imp_flow_2015.pdf}
\caption{Feature importance metrics considering the final flow prediction for CIC-IDS-2017 (left side) and UNSW-NB15 (right side).}
\label{fig:feat_imp}
\end{figure*}
Table~\ref{fig:featRandom} shows our results. The results match to a large extent with the expectations one has when classifying network flows. In particular, the most important features turn out to be the used protocol, packet length and the SYN TCP flag. While the first two features are essential for characterizing flows, a high number of packets with set SYN flag is an important characteristic for port scanning or certain DoS attacks. Also the fact that most of TCP flags do not play an important role in our dataset was expected. It is interesting to note, however, that the interarrival time of packets does not play a crucial role for the detection of attacks.

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{{"../plots/plot2_adv/flows_pred_plots2_outcomes_flows_adv_1.0_notBidirectional_outcomes_0_3.pickle_0_3.pickle_0_Botnet-ARES"}.pdf}
\includegraphics[width=0.48\textwidth]{{"../plots/plot2_adv/flows_pred_plots2_outcomes_flows_adv_1.0_notBidirectional_outcomes_0_3.pickle_0_3.pickle_7_DoS - DDoS-DoS slowloris"}.pdf}
%\includegraphics[width=0.48\textwidth]{{"../plots/plot2_adv/flows_pred_plots2_outcomes_flows_adv_1.0_notBidirectional_outcomes_0_3.pickle_0_3.pickle_11_PortScan-PortScan - Firewall off"}.pdf}
%\includegraphics[width=0.48\textwidth]{{"../plots/plot2_adv/flows_pred_plots2_outcomes_flows_adv_1.0_notBidirectional_outcomes_0_3.pickle_0_3.pickle_1_Brute Force-FTP-Patator"}.pdf}
